---
title: 'Project 3: The first part'
author: "Cassie Boylan, DH Kim, Alexis Mekueko"
date: "10/9/2020"
output:
  slidy_presentation: default
  beamer_presentation: default
header-includes:
- \usepackage{tikz}
- \usetikzlibrary{positioning,shapes.multipart,shapes}
---


```{r setup, include=FALSE}

def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})


```

### Data Source and Loading
Packages used:

```{r load-packages, message=FALSE}


#library(readxl)
library(httr)

#loading some library we might need for this assignment
library(tidyverse) 
#library(openintro)
#head(fastfood)
library(readxl)
library(readr)
library(xlsx)
library(plyr)
library(dplyr)
#library(dice)
# #library(VennDiagram)
# #library(help = "dice")
library(DBI)
library(dbplyr)
library(data.table)
library(rstudioapi)
#rstudioapi::isAvailable()
library(RJDBC)
library(odbc)
library(RSQLite)


```



E-Commerce Data:
```{r, size="tiny"}


retailURL <- 
    "http://archive.ics.uci.edu//ml//machine-learning-databases//00502//online_retail_II.xlsx"


```

Loading and Combining Data 
```{r, size = "tiny", results = "hide"}

GET(retailURL, write_disk(tempFileName <- tempfile(fileext = ".xlsx")))


```



```{r, size="tiny"}

# pretty cleaver here , did not know read cannot grab all sheet at once , and you made it pretty straight forward
retail_sheet_2009 <- read_excel(tempFileName, sheet = "Year 2009-2010")
retail_sheet_2010 <- read_excel(tempFileName, sheet = "Year 2010-2011")
retaildf <- rbind(retail_sheet_2009, retail_sheet_2010)

# I was trying to understand why you have to read the file twice and combined , and from my finding, the read only read one file
# # renaming the original file causes ..Error: `path` does not exist: ‘C:\Users\PETITM~1\AppData\Local\Temp\Rtmp86D16t\fileed47561aa0.xlsx’
# retaildf1 <- read_excel(tempFileName, sheet = "retail_sheets_2009-2011")
# 
# # So, this read 
# retail_sheet <- read_excel(tempFileName)
# view(retail_sheet)
# 
# #export xlsx to project working directory
# write.xlsx(x = retail_sheet,                       # Write xlsx with manual sheet name
#            file = "retail_sheet.xlsx",      
#            sheetName = "Year 2009-2010")
# xlsx(df, "../mydata.xlsx", sheetName = "Sheet1", col.names = TRUE, row.names = TRUE)

#export the retaildf to project working directory, major problem exporting file
#write.xlsx(retaildf, "~/R/Project3/DATA607-Project-3/retaildf.xlsx", sheetName = "Year 2009-2011", col.names = TRUE, row.names = TRUE)

# I think it is possible to write to sql db but it is bit long, this does not work either, I think something wrong with the file
 write.xlsx(x = retaildf,                       # Write xlsx with manual sheet name
            file = "retaildf.xlsx",      
            sheetName = "Year 2009-2010")

 # this export works but I am having trouble opening the file , even the call from db does not get the file , either because too big or maybe my system need a refresh
openxlsx::write.xlsx(x = retaildf, file = "retaildf.xlsx")
getwd()

setwd("~/R/Project3/DATA607-Project-3")



```


### Description of Data
```{r, size = "tiny"}

retaildf


```

## Connecting to project db for importing the files needed 

### Connecting to SQL server
--this connection works but requires password, I am going to comment this block because preventing the knit process.
 --Now we succeeded in reading Arrival_Delays_02_airlines full table into R dataframe.....

 
```{r connection to sql}


 
 #sql connection = con
 
  con <- dbConnect(odbc(), # establishing the connectioon to SQL server to access db
                   Driver = "SQL Server", # server type
                   Server = "ATM\\ATMSERVER", #server name
                   Database = "Data607_Project3_db", # this is one of the db I want to import
                   UID = "Alex", 
                   PWD = rstudioapi::askForPassword("Database password"), # password required
                   Port = 1433)  # port connection
 
  dbListFields(con, "retaildf")  # loading the db into R for manipulation and analysis
  retaildf1 <- dbReadTable(con, "retaildf") 
  retaildf1
  
  

```



### E-R Diagram

\tikzset{basic/.style={
        draw,
        rectangle split,
        rectangle split parts=2,
        rectangle split part fill={blue!20,white},
        minimum width=2.5cm,
        text width=2cm,
        align=left,
        font=\itshape
    },
    Diamond/.style={ diamond, 
                        draw, 
                        shape aspect=2, 
                        inner sep = 2pt,
                        text centered,
                        fill=blue!10!white,
                        font=\itshape
                      }}
\begin{tikzpicture}
\node[basic] (product) 
{product
\nodepart{second}
\underline{product\_id}\\
product\_name};
\node[basic,right=2cm of product] (invoice) 
{invoice
\nodepart{second}
\underline{invoice\_id}\\
customer\_id\\
invoice\_date};
\draw (product) -- (invoice) ;
\node[basic,right=2cm of invoice] (invoiceitem) 
{invoiceitem
\nodepart{second}
\underline{invoice\_id}\\
\underline{product\_id}\\
price\\
quantity};
\draw (invoice) -- (invoiceitem) ;
\node[basic,below=1.5cm of invoice] (customer) 
{customer
\nodepart{second}
\underline{customer\_id}\\
	country};
\draw (invoice) -- (customer) ;
\end{tikzpicture}

